Topological approach to finding blackholes in directed networks

### 2019-12-02 blackholes/pavt/article.tex

As it was described in the Known Issues section, large SCCs waste lots of computational time without adding any new blackholes. 
For certain graph types (RMAT, SmallWorld) it can be crucial, because one SCC can contain up to 100\% of all graph's vertices. 
In such a case, it would be nice to consider large SCC as a single vertex, aggregating all incoming and outcoming peripheral edges
of original SCC.
On the preprocessing stage of the algorithm we reduce every SCC to a single vertex. The algorithm is not new and known as a graph condensation.

@@

\begin{definition}
Closure of vertex v is a set of all nodes reachable from v, including v.
\end{definition}

>>>>

As it was described in the Known Issues section, large SCCs waste lots of computational time without adding any new blackholes. 
For certain graph types (RMAT, SmallWorld) it can be crucial, because one SCC can contain up to 100\% of all graph's nodes. 
In such a case, it would be nice to consider large SCC as a single node, aggregating all incoming and outcoming peripheral edges
of original SCC.
On the preprocessing stage of the algorithm we reduce every SCC to a single node. The algorithm is not new and known as a graph condensation.

@@

\begin{definition}
Closure of node v is a set of all nodes reachable from v, including v.
\end{definition}
